%# -*- coding:utf-8 -*-
\begin{publications}

\section*{个人简历：}
姓名：陈隆 \qquad\qquad\qquad\qquad\qquad\qquad 出生年月：1993年12月

民族：汉族 \qquad\qquad\qquad\qquad\qquad\qquad 政治面貌：中共党员

%邮箱：longc@zju.edu.cn \qquad\qquad\qquad\hspace{0.3em}  个人主页：\href{http://zjuchenlong.github.io}{zjuchenlong.github.io} 
 
\vspace{1.0em}
教育经历：
\begin{asparaitem}                                                
\item{2015.09 – 2020.06： \quad 浙江大学 \qquad\qquad 计算机科学与技术学院 \qquad  博士}
\item{2018.07 – 2019.05： \quad 新加坡南洋理工大学（学术新星计划资助） \quad 访问学者}
\item{2017.08 – 2018.02： \quad 美国哥伦比亚大学（研究生院校派资助） \qquad 访问学者}
\item{2011.09 – 2015.06： \quad 大连理工大学 \qquad 信息与通信工程学院 \qquad\quad 本科}  
\end{asparaitem}

\section*{发表学术论文：}

% review version
% \begin{enumerate}
% \item{
% 第一作者. IEEE Conference on Computer Vision and Pattern Recognition (CVPR), 2017.（CCF A 类）
% }

% \item{
% 第一作者. IEEE Conference on Computer Vision and Pattern Recognition (CVPR), 2018.（CCF A 类）
% }

% \item{
% 第一作者. IEEE International Conference on Computer Vision (ICCV), 2019.（CCF A 类）
% }

% \item{
% 第一作者. Thirty-Fourth AAAI Conference on Artificial Intelligence (AAAI), 2020.（CCF A 类）
% }

% \item{
% 第一作者. IEEE Conference on Computer Vision and Pattern Recognition (CVPR), 2020.（CCF A 类）
% }

% \item{
% 第二作者. Conference on Empirical Methods in Natural Language Processing (EMNLP), 2019.（CCF B 类）
% }

% \item{
% 第二作者. ACM International Conference on Multimedia (ACM MM), 2019.（CCF A 类）
% }

% \item{
% 第四作者. Neural Processing Letters, 2019. (SCI期刊). 
% } 
% \end{enumerate}



\begin{enumerate}
\item{
\textbf{Long Chen}, Hanwang Zhang, Jun Xiao, Wei Liu, Shih-Fu Chang.
Zero-Shot Visual Recognition using Semantics-Preserving Adversarial Embedding Networks [C].
IEEE Conference on Computer Vision and Pattern Recognition (CVPR), 2018.
（第一作者， CCF-A类）
}

\item{
\textbf{Long Chen}, Hanwang Zhang, Jun Xiao, Xiangnan He, Shiliang Pu, Shih-Fu Chang.
Counterfactual Critic Multi-Agent Training for Scene Graph Generation [C].
IEEE International Conference on Computer Vision (ICCV), 2019.
（第一作者， CCF-A类）
}

\item{
\textbf{Long Chen}, Hanwang Zhang, Jun Xiao, Liqiang Nie, Jian Shao, Wei Liu, Tat-Seng Chua.
SCA-CNN: Spatial and Channel-wise Attention in Convolutional Networks for Image Captioning [C].
IEEE Conference on Computer Vision and Pattern Recognition (CVPR), 2017.
（第一作者，CCF-A类）
}

\item{
\textbf{Long Chen}, Chujie Lu, Siliang Tang, Jun Xiao, Dong Zhang, Chilie Tan, Xiaolin Li.
Rethinking the Bottom-Up Framework for Query-based Video Localization [C].
Thirty-Fourth AAAI Conference on Artificial Intelligence (AAAI), 2020.
（第一作者，CCF-A类）
}

\item{
\textbf{Long Chen}, Xin Yan, Jun Xiao, Hanwang Zhang, Shiliang Pu, Yueting Zhuang.
Counterfactual Samples Synthesizing for Robust Visual Question Answering [C].
IEEE Conference on Computer Vision and Pattern Recognition (CVPR), 2020.
（第一作者，CCF-A类）
}

\item{
Chujie Lu, \textbf{Long Chen}, Chilie Tan, Xiaolin Li, Jun Xiao.
DEBUG: A Dense Bottom-Up Grounding Approach for Natural Language Video Localization [C].
In Conference on Empirical Methods in Natural Language Processing (EMNLP), 2019.
（第二作者， CCF-B类）
}

\item{
Lei Meng, \textbf{Long Chen}, Xun Yang, Dacheng Tao, Hanwang Zhang, Chunyan Miao, Tat-Seng Chua.
Learning Using Privileged Information for Food Recognition [C].
In ACM International Conference on Multimedia (ACM MM), 2019.
（第二作者，CCF-A类）
}

\item{
Xingchen Li, Xiang Wang, Xiangnan He, \textbf{Long Chen}, Jun Xiao, Tat-Seng Chua.
Hierarchical Fashion Graph Network for Personalised Outfit Recommendation [C].
ACM SIGIR Conference on Research and Development in Information Retrieval (SIGIR), 2020.
（第四作者，CCF-A类）
}

\item{
Yunan Ye, Zhou Zhao, Yimeng Li, \textbf{Long Chen}, Jun Xiao, Yueting Zhuang.
Video Question Answering via Attribute-Augmented Attention Network Learning [C].
ACM SIGIR Conference on Research and Development in Information Retrieval (SIGIR), 2017.
（第四作者，CCF-A类）
}


\item{
Shaoning Xiao, Yimeng Li, Yunan Ye, \textbf{Long Chen}, Shiliang Pu, Zhou Zhao, Jian Shao, Jun Xiao.
Hierarchical Temporal Fusion of Multi-grained Attention Features for Video Question Answering [J]. 
Neural Processing Letters, 2019. 
（第四作者，SCI期刊）
} 
\end{enumerate}

\section*{参与项目：}
\begin{enumerate}
\item{高度真实感并行绘制技术和引擎, 重大研究计划项目（课题子任务）, 纵向, 科技部, 2017YFGX030023, 2017.07-2020.12。}
\item{人工智能技术在特定领域的应用研究与示范，浙江省2018年度重点研发计划项目，2018.01-2020.12。}
\item{复杂视觉场景智能感知与内容生成研究，浙江省自然科学基金杰出青年项目，2019.01-2022.12。}
\item{视觉内容智能感知与生成方法研究，国家自然科学基金面上项目，2020.01-2023.12。}
\item{云边协同的智能视频大数据边缘计算，国家自然科学基金重点项目，2020.01-2023.12。}
\end{enumerate}


\section*{所获荣誉：}

\begin{itemize}
    
\item 2016-2017学年：优秀研究生、三好研究生、国睿奖学金

\item 2017-2018学年：优秀研究生、浙江大学博士研究生学术新星

\item 2018-2019学年：优秀研究生、三好研究生、倪继红奖学金

\item 2019-2020学年：浙江省优秀毕业研究生、浙江大学优秀毕业研究生、毕业研究生奖学金

\end{itemize}

\end{publications}
